\cvsection{Experience}
\begin{cventries}
  \cventry
    {Lead Software Engineer}
    {Hudson's Bay Company}
    {Vancouver, Canada (Remote)}
    {Aug. 2018 - PRESENT}
    {
      \begin{cvitems}
        \item {Engineer lead of a team of 3 experienced developers each with
            multiple years of industry experience}
        \item {Directed team towards adopting a functional code base with Cats + FS2}
        \item {Currently architecting and driving a cross-team, multi-service
            initiative on track to save the company over \$1M USD anually}
      \end{cvitems}
    }
  \cventry
    {Software Engineer II}
    {}
    {}
    {Nov. 2017 - Aug. 2018}
    {
      \begin{cvitems}
        \item {Individually integrated inventory management systems across banners as part of
          the shared selling initiative, driving double digit growth for the
          Gilt banner}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {}
    {}
    {July 2016 - Nov. 2017}
    {
      \begin{cvitems}
        \item {Refactored mission critical service to use Postgres instead of Mongo; strategized deployment resulting in no downtime}
        \item {Modified delivery window calculation to include customer location improving checkout conversion across many states}
      \end{cvitems}
    }
  \cventry
    {Platform Engineer Intern}
    {Strava}
    {San Francisco, USA}
    {Aug. 2015 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Optimized user characteristics processing with development of Scala service leveraging Spark}
        \item {Designed and deployed Spark cluster to production atop of Apache Mesos}
        \item {Scaffolded machine-learning service to classify and mitigate spam posted throughout the site}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Gilt Groupe}
    {New York City, USA}
    {Jan. 2015 - Apr. 2015}
    {
      \begin{cvitems}
        \item {Designed and built a public API with Scala + Play as part of the global redistribution team to provide inventory and catalog information to redistribution partners, increasing global incremental revenue by more than 40\%}
        \item {Integrated existing Scala services with the warehouse management system using Apache Camel and RabbitMQ}
        \item {Aided in migration process to AWS + Docker infrastructure}
      \end{cvitems}
    }
\end{cventries}
