\documentclass{cv}

\themeColor{cvDarkBlue}
\name{Christopher Poenaru}
\tagline{Computer Engineer {\hspace{5pt}--\hspace{5pt}}  Functional Programmer {\hspace{5pt}--\hspace{5pt}} Triathlete {\hspace{5pt}--\hspace{5pt}} Rock Climber}
\email{kiambogo@gmail.com}
\web{chrispoenaru.com}
\linkedin{chrispoenaru}
\github{kiambogo}

\skills{
  \skillsItem{Scala}
  \skillsItem{Go}
  \skillsItem{Haskell}
  \skillsItem{Java}
  \skillsItem{AWS + Heroku}
  \skillsItem{Postgres}
  \skillsItem{Redis}
  \skillsItem{Cassandra}
  \skillsItem{MongoDB}
}

\projects{
  \cvEntry{Scrava}{}{\href{https://github.com/kiambogo/scrava}{\faGithubSquare \hspace{0.5mm} kiambogo/scrava}}{}{
    \entryItems{
      \item{Community recognized, open-source Scala client for the Strava API}
    }
  }
  \vspace{5pt}
  \cvEntry{Road Quality}{}{\href{https://github.com/trifectalabs/roadquality}{\faGithubSquare \hspace{0.5mm} trifectalabs/roadquality}}{}{
    \entryItems{
      \item{Crowdsourced road quality and traffic safety data for cyclists}
      \item{Allows cyclists to rate sections of a road or path to build a
        community driven topology of the safest cycling routes}
      \item{API and pathing logic implemented in Scala; custom mapping engine built with Rust}
    }
  }
}

%TODO: dont need this section, can just use the existing commands
\contact{
    \contactItem{mailto:\myEmail}{\myEmail}{\faEnvelope}
    \contactItem{https://\myWeb}{\myWeb}{\faHome}
    \contactItem{https://www.linkedin.com/in/\myLinkedin}{\myLinkedin}{\faLinkedin}
    \contactItem{https://github.com/\myGithub}{\myGithub}{\faGithub}
}

\experience{
  \cvEntry{MasonHub}{Los Angeles, CA (Remote)}{Software Engineer}{Jan. 2019 - Jan. 2021}{
    \entryItems{
      \item{Third engineer, responsible for designing, building, and owning multiple core systems that scaled the company from 0 clients to 35+ within 2 years}
      \item{Constructed Shopify integration, reducing technical client onboarding time to minutes}
      \item{Architected fault-tolerant, scalable printer management system allowing for custom supply chain documents. Successfully printed over 250,000+ documents}
      \item{Refactored critical, production database schema reducing average inventory ledger query times to 2.5ms and bulk order processing time to 160ms}
    }
  }
  \cvEntry{Hudson's Bay Company}{New York, NY (Remote)}{Lead Software Engineer}{Aug. 2018 - Jan. 2019}{
    \entryItems{
      \item {Engineering lead of a team of 4 intermediate and senior level developers}
      \item {Directed team towards adopting a functional code base with Scala Cats + FS2}
      \item {Architected a multi-service initiative to optimize safety stock levels and reduce order shorting}
    }
  }
  \cvEntry{}{}{Software Engineer II}{Nov. 2017 - Aug. 2018}{
    \entryItems{
      \item {Conflated inventory management systems across banners as part of
        the shared selling initiative, driving double-digit growth for the Gilt banner}
    }
  }
  \cvEntry{}{}{Software Engineer}{July 2016 - Nov. 2017}{
    \entryItems{
      \item {Refactored mission critical service to use Postgres instead of Mongo; strategized deployment resulting in zero downtime}
      \item {Modified website delivery window calculation to include customer location, improving checkout conversion across many US states}
    }
  }
  \cvEntry{Strava}{San Francisco, CA}{Platform Engineer Intern}{Aug. 2015 - Dec. 2015}{
    \entryItems{
      \item{Optimized user characteristics processing with development of Scala service leveraging Spark}
      \item{Designed and deployed Spark cluster to production atop of Apache Mesos}
    }
  }
  \cvEntry{Gilt Groupe}{New York, NY}{Software Engineering Intern}{Jan. 2015 - Apr. 2015}{
    \entryItems{
      \item {Designed and built a public API with Scala + Play as part of the global redistribution team to provide inventory and catalog information to redistribution partners, increasing global incremental revenue by more than 40\%}
    }
  }
}

\education{
  \cvEntry{University of Waterloo}{Waterloo, Canada}{BASc. Computer Engineering}{2011-2016}{}
}

\begin{document}
    {\mkHeader}
    {\mkBody}
\end{document}
