\cvsection{Experience}
\begin{cventries}
  \cventry
    {Platform Engineer Intern}
    {Strava}
    {San Francisco, USA}
    {Aug. 2015 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Optimized user characteristics processing with development of Scala service leveraging Spark}
        \item {Designed and deployed Spark cluster to production atop of Apache Mesos}
        \item {Scaffolded machine-learning service to classify and mitigate spam posted throughout the site }
        \item {Architected }        
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Gilt Groupe}
    {New York City, USA}
    {Jan. 2015 - Apr. 2015}
    {
      \begin{cvitems}
        \item {Designed and built a public API with Scala + Play as part of the global redistribution team to provide inventory and catalog information to redistribution partners, increasing global incremental revenue by more than 40\%}
        \item {Integrated existing Scala services with the warehouse management system using Apache Camel and RabbitMQ}
        \item {Aided in migration process to AWS + Docker infrastructure}
        \item {Contributed to several community-renowned Gilt open-source projects including APIDoc}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Gilt Groupe}
    {New York City, USA}
    {Apr. 2014 - Aug. 2014}
    {
      \begin{cvitems}
        \item {Engineered service layer application written in Scala with Play, Akka, and Salat (MongoDB)}
        \item {Designed and implemented a service for vendor provided images, resulting in reducing vendor on-boarding time}
        \item {Constructed an algorithmic process to pass images for editing, resulting in time savings of over 90\% per vendor}
        \item {Frontend development of Gilt Direct webpage using Play and AngularJS}      
      \end{cvitems} 
    }
  \cventry
    {Technology Information Risk Intern}
    {Morgan Stanley}
    {Montreal, Canada}
    {Sep. 2013 - Dec. 2013}
    {
      \begin{cvitems}
        \item {Developed security modules for PingFederate SAML server written in Java}
        \item {Integrated Kerberos, SAML, and Siteminder single sign-on solutions}
        \item {Designed and programmed web applications using Java, Javascript, NodeJS}
      \end{cvitems}
    }
\end{cventries}
